---
title: "Reproducible Research: Peer Assessment"
output: html_document
date: '2022-08-21'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
knitr::opts_chunk$set(collapse = T, comment = "#>")
options(tibble.print_min = 4L, tibble.print_max = 4L)
```

## Contents

The scope of project is to analyze  personal movement using activity monitoring devices and draw conclusions and insights based on findings. 

Data used in research

Dataset: Activity monitoring data [52K]
steps: Number of steps taking in a 5-minute interval (missing values are coded as NA)
date: The date on which the measurement was taken in YYYY-MM-DD format
interval: Identifier for the 5-minute interval in which measurement was taken


```{r}
library(dplyr)
library(ggplot2)
library(data.table)

data2 <- read.csv("C:\\Users\\sskhirtladze\\Desktop\\My Skills\\Data science\\Course_5_Reproductible research\\Exam1\\repdata_data_activity\\activity.CSV", header=TRUE, stringsAsFactors=FALSE)
data3<-na.omit(data2)
data3$date<-as.factor(as.character(data3$date))

total_steps <- data3 %>%
group_by(date) %>%
summarise(daily_steps = sum(steps, na.rm = TRUE))

ggplot(total_steps, aes(daily_steps)) + geom_histogram(binwidth = 2000) + xlab("Total number of steps taken each day") + ylab("Frequency")

interval_steps <- data2 %>% 
  group_by(interval) %>%
  summarise(steps = mean(steps, na.rm =TRUE))

ggplot(data=interval_steps, aes(x=interval, y=steps)) + geom_line() + xlab("5-minute intervals") +
ylab("Average number of steps taken")


meanSteps <- summarize(data3, meanSteps = round(mean(steps, na.rm = T)))

imputed_total_steps <- data3 %>% 
  group_by(date) %>%
  summarise(daily_steps = sum(steps))

ggplot(imputed_total_steps, aes(daily_steps)) + geom_histogram(binwidth = 2000) + xlab("Total number of steps taken each day") +   ylab("Frequency")

day_of_week <- data3 %>% 
  mutate(weekday_or_weekend = case_when(wday(date) %in% 2:6 ~ "Weekday",wday(date) %in% c(1,7) ~ "Weekend")) %>% select(-date) %>%
 group_by(interval, weekday_or_weekend) %>% 
 summarise(steps = mean(steps))

 ggplot(day_of_week, aes(interval, steps)) + geom_line() +facet_wrap(~weekday_or_weekend, nrow = 2) +xlab("5-Minute intervals") +  ylab("Average number of steps")

knitr::opts_chunk$set(echo = TRUE)
```

